Comparison of clusters to cell types for `r params$library_id`

### 2024-12-06 analyses/cell-type-ewings/template_notebooks/clustering-workflow/02-clustering-celltypes.Rmd
use nn not k

@@

Finally, we will look at the expression of marker genes across each cluster for each value of `k`. 
In these plots, each row shows the distribution of the specified marker genes in that cluster. 
Each panel is labeled with the marker gene expression being plotted.

>>>>

## Number of clusters

Below is a table showing the number of clusters found for each value of `nn`.

```{r}
clusters_df |> 
  dplyr::select(nn, cluster) |> 
  dplyr::group_by(nn) |> 
  dplyr::summarise(num_of_clusters = length(unique(cluster)))
```

@@

Finally, we will look at the expression of marker genes across each cluster for each value of `nn`. 
In these plots, each row shows the distribution of the specified marker genes in that cluster. 
Each panel is labeled with the marker gene expression being plotted.
